A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-31 paper.tex
Fix the irrelevant context in digital identity

Centralized identity model may have single point failure in identifier management and security issues like data leakage. With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.

>>>>

The centralized identity model may have single point failure in identifier management and security issues like data leakage. With sensitive information holding on certain authorities, the leakage caused by cyber attacks or unscrupulous organizations trading user data damage the users' privacy. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others. The decentralized identity model give back the controls of data to users that can resolve the aforementioned concerns in the centralized one.
